\cvsection{Experience}
\vspace{-8pt}
\begin{cventries}
  \cventry
  {Faculty of Forestry and Wood Sciences - Czech University of Life Sciences Prague}
  {Postdoctorat Fellow in forest spatial pattern}
  {Nov. 2015 - PRESENT}
    {Prague, Czech Republic}
{
    \begin{cvitems}
    \item []{\textnormal{Dynamics of temperate moutain forests in
          central and eastern Europe (Carpathians). Focusing to link
          the forest spatial pattern to the disturbance
          history. Working in M. Svoboda team's}}
      \begin{itemize}[label=$\bullet$,topsep=2pt]
      \item {Spatial analysis (point pattern using latest rank
          envelope test development)}
    \item {RandomForest analyses}
    \item {R programming (creating functions \& packages,
        parallelization computing, use SQL database within R)}
    \item {Data mining}
      \end{itemize}
      \end{cvitems}
    }

\vspace{-3pt}
    \cventry
  {University of Québec at Montréal}
  {Teaching assistant}
  {Feb. – Aug. 2014 \& Jan. - Dec. 2015}
    {Montréal, Canada}
{
    \begin{cvitems}
    \item []{\textnormal{About 200 hrs. as a teaching assistant for undergraduate and PhD
          students for the courses BIA 1700 Organisms and environment
          (two times), BIO 6600 Fieldwork methodology in ecology (two
          times) – Vegetation component and ENV 9501 Environmental
          systems dynamic (two times)}}
    \end{cvitems}
  }


  \cventry
  {Centre for Forest Research - University of Québec in Abitibi-Témiscamingue}
  {PhD in Environmental Sciences on the natural disturbances dynamic
    of the Temiscamingue temperate deciduous forest}
  {Jan. 2011 - Aug. 2015}
    {Qc, Canada}
    {
      \begin{cvitems}
      \item []{\textnormal{Worked in collaboration with my supervisor
             H. Asselin (UQAT) and co-supervisors F.
            Doyon (ISFORT,/UQO) and Y. Bergeron (Industrial Research Chairs NSERC, UQAT-UQÀM)}}
      \begin{itemize}[label=$\bullet$,topsep=2pt]
        \item {Reconstitution and modeling of the naturals disturbances dynamic of the sugar maple – yellow birch bioclimatic domain at stand and landscape scale}
        \item {\textbf{Dendrochronology}, statistical and \textbf{spatial} (point
            pattern) analysis using R software and LANDIS-II (forest landscape
            modeling)}
      \end{itemize}
      \end{cvitems} 
    }


    \cventry
  {ENTPE - Environmental Science Laboratory \& CNRS Unit 5023}
  {Master training on the lentic aquatic ecosystem organism responses representative to a chronic exposition to percolated water of contaminated marine sediment.}
  {Jan. 2010 - Jun. 2010}
    {Vaux-en-Velin, France}
{
  \begin{cvitems}
          \begin{itemize}[label=$\bullet$,topsep=2pt]
    \item {Organization and monitoring of a long experimentation (3 months)}
    \item {Statistical analyses with R software – Mixed models, PCA, glm}
          \end{itemize}
\end{cvitems} 
  }


  \cventry
  {CNRS Unit 5558 - Biometry and Evolutionary Biology laboratory}
  {Training on the impact of an organophosphorus pesticide on the interspecific mating of two trichogramma species, \textit{Trichogramma semblidis} and \textit{T. evanescens.}}
  {Feb. 2009 - Jun. 2009}
    {Lyon, France}
{
  \begin{cvitems}
              \begin{itemize}[label=$\bullet$,topsep=2pt]
    \item {Organization and adaptation of a new protocol}
    \item {Statistical analyses with R software – Chi-square test, logrank test (Survival analysis)}
              \end{itemize}
\end{cvitems} 
}


      \cventry
  {Forest and Ecosystem Science - University of Melbourne}
  {Training on the phylogeography of \textit{Eucalyptus regnans}, \textit{E. Delegatensis} and \textit{E. Obliqua} population’s}
  {Feb. 2008 - Aug. 2008}
    {Melbourne, Australia}
{
    \begin{cvitems}
    \item []{\textnormal{Worked in collaboration with G. Bossinger and P. Nevill}}
    \              \begin{itemize}[label=$\bullet$,topsep=2pt]
item {Participated to a scientific project from beginning to end
        – Field work in difficult conditions in Australian Alps – Oral
        report in English}
          \item {Molecular biology – DNA extraction, PCR (use of microsatellites markers) and others lab works}
              \end{itemize}
\end{cvitems} 
  }


  \cventry
  {CNRS Unit 5558 - Biometry and Evolutionary Biology laboratory}
  {Training on the roe population repartition in an Experimentation and Study Territory}
  {Oct. 2007 - Jan. 2008}
    {Lyon, France}
{
  \begin{cvitems}
              \begin{itemize}[label=$\bullet$,topsep=2pt]
    \item {Studies of population genetics and field work (Capture – Mark – Recapture)}
    \item {Computerizing, structuring and analyses of an extensive dataset (over 30 years) with R software – linear models}
              \end{itemize}
\end{cvitems} 
  }
\end{cventries}
